method

### 2022-01-26 06_Paper/ER-ED/method.Rmd
added loop for data import

# new empty frame to store files into
data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
                     Lev = double())
```

>>>>

# new empty frame to store files into
data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
                     Lev = double())

# store EMG data in data_EMG frame
for (i in 1:length(datalist_EMG)) {

  tmp = data.frame(datalist_EMG[[i]][["participant"]], 
                   datalist_EMG[[i]][["Segment"]], 
                   datalist_EMG[[i]][["T0T6000Corr-ASNM"]], 
                   datalist_EMG[[i]][["T0T6000Lev-ASNM"]])
  colnames(tmp) = names(data_EMG)

  data_EMG = rbind(tmp, data_EMG)

#rownames(data_ER) = 1:nrow(data_ER)

```
